---
title: "TDW"
author: "Turkan Sevgili"
date: "13 November 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Travel Weather Data

Source: [Tidyverse Recap](https://mef-bda503.github.io/files/tidyverse_recap_p1.html)

First I had a quick review of Travel Weather data and finished all exercises.

```{r,message=FALSE}
#Load package tidyverse
library(tidyverse)

# Begin by loading the dataset
library(readr)
load("D:/Users/tkartalkaya/Desktop/travel_weather.RData")

travel_weather %>% tbl_df()

glimpse(travel_weather)
```


###select/rename
```{r}

1
travel_weather %>% select(year, month, day, Venice)
2
travel_weather %>% select(Venice:Amsterdam)
3
travel_weather %>% select(-NYC, -London)
4
travel_weather %>% rename(`New York` = NYC)
```


###arrange
```{r}

1
travel_weather %>%
  arrange(NYC)
2
travel_weather %>%
  arrange(NYC,desc(Amsterdam))
3
travel_weather %>%
  arrange (desc(year),desc(month),desc(day))
4
travel_weather %>%
  arrange(London - Amsterdam)
```

###mutate/transmute
```{r}

1
travel_weather %>%
  mutate(VAdiff = Venice - Amsterdam)
2
travel_weather %>%
  mutate(VwarmerA = Venice > Amsterdam)
3
travel_weather %>%
  transmute(year,month,day,
            VwarmerA = ifelse(Venice > Amsterdam,'warmer', 'colder'))
```

###group_by/summarise
```{r}

1
travel_weather %>%
  summarise(Venice_mean=mean(Venice),NYC_mean=mean(NYC))
2
travel_weather %>%
  group_by(month) %>%
  summarise(Amsterdam_mean=round(mean(Amsterdam),2))
3
travel_weather %>%
  group_by(year,month) %>%
  summarise(AwarmerN_n=sum(Amsterdam > NYC))
4
travel_weather %>%
  group_by(year,month) %>%
  summarise(London_min=min(London),London_median=median(London),London_max=max(London))
```

##Advanced Examples

###Lead and Lag
```{r}
travel_weather %>%
  transmute(year,month,day,Amsterdam,A_prev=lag(Amsterdam),A_next=lead(Amsterdam),
            A_prev_diff=Amsterdam-A_prev,A_next_diff=Amsterdam-A_next)
```

###slice
```{r}
travel_weather %>%
  slice(1:3)

travel_weather %>%
  group_by(year) %>%
  slice(1:3)
```

###Gather and Spread
```{r}
#Transform to long format by melting the data
#Though you should not include date columns
travel_weather_long <-
  travel_weather %>%
  gather(key=City,value=Temperature,-year,-month,-day)
travel_weather_long

#Now group by and summarise to get average temperatures for each city and month
travel_weather_long %>%
  group_by(month,City) %>%
  summarise(temp_avg=round(mean(Temperature))) %>%
  #Now spread the months to the columns
  spread(month,temp_avg)
```

###_all and _at prefixes
```{r}
#Method 1
travel_weather %>%
  select(Amsterdam:Venice) %>%
  summarise_all(funs(round(mean(.))))

#Method 2
travel_weather %>%
  summarise_at(vars(Amsterdam:Venice),funs(round(mean(.))))

#Method 2
travel_weather %>%
  mutate_at(vars(Amsterdam,London,Venice),funs(diff_NYC=abs(NYC-.))) %>%
  select(-Amsterdam,-London,-Venice)
```


## Final Exercises

My answers of the final exercices are shown below.

1. Return the dates which Amsterdam is strictly warmer than London but strictly colder than Venice

```{r}
travel_weather %>%
  filter(  (Amsterdam>London) & (Amsterdam<Venice))
```


2. For each month of each year calculate the average difference between NYC and Amsterdam for the days NYC is strictly warmer than Amsterdam, rounded by 1 decimal. Arrange from the highest difference to the lowest.

```{r}
travel_weather %>%
    filter(NYC>Amsterdam)%>%
    group_by(year,month)%>%
    summarise_at(vars(Amsterdam,NYC),funs(round(mean(.),1)))%>%
    mutate(NYCwA_diff=NYC-Amsterdam)%>%
    select(-Amsterdam,-NYC)%>%
    arrange(desc(NYCwA_diff))
```


3. Return the warmest city and its temperature of each day.

```{r}
travel_weather %>%
  gather(key=City,value=Temperature, -year, -month, -day) %>%
  group_by(year, month, day) %>%
  mutate(max_temp =max(Temperature)) %>%
  filter(Temperature==max_temp)  %>%
  arrange(year,month,day) %>%
  select(year, month, day,City,Temperature)
```