---
title: "Interesting R Examples"
author: "Türkan Sevgili - BDA 503 - Fall 2017"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="pdf_document")
rmarkdown::render("/Users/berkorbay/Dropbox/Courses_given/MEF_BDA_503_2017F/Guidelines/example_homework_1.Rmd",output_format="html_document")
```

1. [A Very Extensive Zillow Exploratory Analysis](https://www.kaggle.com/captcalculator/a-very-extensive-zillow-exploratory-analysis)

    This example is about the leading real estate marketplace Zillow. It’s very informative and expansive analysis. It is also a Kaggle Kernel, which is a very good source for this kind of example R codes. It helped a lot with data visualization.
    
2. [Exploratory Analysis Rossmann](https://www.kaggle.com/thie1e/exploratory-analysis-rossmann)

    This post really helps to understand the data better. Amazing detailed study and excellent analysis. It is clear and excellent for R-beginner (like me) 
    
3. [How to use text mining with R](http://opensourceforu.com/2017/02/text-mining-with-r)

    It is a text mining and very thorough documentation .It's much appreciated.

4. [Crafting A Powerpoint Presentation With R](http://lenkiefer.com/2017/09/23/crafting-a-powerpoint-presentation-with-r/)

    I think write-up like this helps a lot to master the skills needed. It is a good tutor and very helpful.
    
5. [Radio Swiss classic program](http://www.masalmon.eu/2017/04/23/radioswissclassic/)

    It is a well explained study. There is excellent introduction with great detail. 
